Trait plasticity and covariance along a continuous soil moisture gradient

### 2020-02-14 FVT Manuscript/manuscript.Rmd
commit

Significant interactions between genotype and environmental parameters in a final model indicate the presence of genetic variation for plasticity (GxE) [@via1985genotype]. For those GxE interactions where the environmental parameter is non-linear, significant GxE indicates genetic variation for the shape of reaction norms. SLA showed a significant interaction between genotype and soil moisture in _B. distachyon_. In _B. sylvaticum_, nitrogen content, carbon to nitrogen ratio, above ground green area, and root to shoot ratio all showed significant interactions between genotype and soil moisture (Table \@ref(tab:models), Figure \@ref(fig:curves)). In each of these cases, the interaction between genotype and environment involved a non-linear environmental predictor, indicating not only variation for the magnitude of plasticity (i.e. slope) but also variation in the shape of responses.

>>>>

Significant interactions between genotype and environmental parameters in a final model indicate the presence of genetic variation for plasticity (GxE) [@via1985genotype]. For those GxE interactions where the environmental parameter is non-linear, significant GxE indicates genetic variation for the shape of reaction norms. SLA showed a significant interaction between genotype and soil moisture in _B. distachyon_. In _B. sylvaticum_, nitrogen content, carbon to nitrogen ratio, and root to shoot ratio all showed significant interactions between genotype and soil moisture (Table \@ref(tab:models), Figure \@ref(fig:curves)). In each of these cases, the interaction between genotype and environment involved a non-linear environmental predictor, indicating not only variation for the magnitude of plasticity (i.e. slope) but also variation in the shape of responses.
